\Title

### 2022-09-29 Grimaldi-etal-BiolCybernetics.tex
Introduction: 1.3

In this work, we study the emergence of such spatiotemporal spike motifs when training a single layer of spiking neurons on a supervised classification task (\seeFig{motion_task}). The paper is organized as follows. We develop a theroretically-defined SNN capable of learning heterogeneous delays which we first evaluate on an event-based synthetic dataset. We will first detail the methodology by defining the core spike mechanism using heterogeneous delays. We will then formally define the computational task of motion detection. This will allow us to formalize the  spiking neuron used to learn the model and test its effectiveness. We aim at applying this model to a real-world task of motion detection which we will first define. Then we will show how the model can be adapted to solve the motion detection task. In the results section, we will detail the emergent structure of the model solving the task and show in particular the similarities with neurobiological observations. We will also test the network with classical stimuli used in neuroscience, and in particular the frequency or contrast responses.  We will also study the efficiency of the motion detection mechanism and in particular its resilience to synaptic weight pruning. This will allow us to show how such a model can provide an effective solution to the energy/accuracy trade-off.  Finally, we will conclude by highlighting the main contributions of this paper, while defining some limitations. This will open up perspectives for future SNNs.  In particular, as neuromorphic devices are by design good candidates for integrating computations over time, we highlight the fact that this event-driven algorithm is transferable to this type of hardware.

>>>>

In this work, we study the emergence of spatio-temporal spiking motifs when training a single layer of spiking neurons on a semi-supervised classification task (\seeFig{motion_task}). The paper is organized as follows. We develop a theoretically defined SNN capable of learning from heterogeneous delays that we first evaluate on a synthetic event-based dataset. We first detail the methodology by defining the basic mechanism of spiking neurons that utilize heterogeneous delays. This will allow us to formalize the spike neuron used to learn the model's parameters and test its effectiveness. We aim to apply this model to a realistic motion detection task which we will first define. Then, we will show how the model can be adapted to solve the motion detection task. In the results section, we will detail the emergent structure of the model solving the task and show in particular the similarities with neurobiological observations. We will also test the network with classical stimuli used in neuroscience, and in particular with frequency or contrast responses.  We will also study the efficiency of the motion detection mechanism and in particular its resilience to synaptic weight pruning. This will allow us to show how such a model can provide an efficient solution to the energy/accuracy trade-off.  Finally, we will conclude by highlighting the main contributions of this paper, while defining some limitations. This will open perspectives for future SNNs.  In particular, as neuromorphic devices are by design good candidates for integrating computations over time, we highlight the fact that this event-driven algorithm is transferable to this type of hardware.
